### 2015-02-22 zoldatoff/tex/pattern discovery/lecture02.tex
Технические доработки в документе

%--
\subsection{Expressing Patterns in Compressed Form}
Solution 1: \textbf{Closed patterns:} \textit{A pattern (itemset) X is closed if X is frequent, and there exists no super-pattern $Y \supset X$, with the same support as X}.\\

Closed pattern is a lossless compression of frequent patterns.\\

Solution 2: \textbf{Max-patterns:} \textit{A pattern X is a max-pattern if X is frequent and there exists no frequent super-pattern $Y \supset X$}.\\

Max-pattern is a lossy compression!

>>>>

%--
\subsection{Expressing Patterns in Compressed Form}
\begin{definition}
\textbf{Closed patterns:} \textit{A pattern (itemset) X is closed if X is frequent, and there exists no super-pattern $Y \supset X$, with the same support as X}.
\end{definition}
Closed pattern is a lossless compression of frequent patterns.

\begin{definition}
\textbf{Max-patterns:} \textit{A pattern X is a max-pattern if X is frequent and there exists no frequent super-pattern $Y \supset X$}.
\end{definition}
Max-pattern is a lossy compression!

### 2015-02-22 zoldatoff/tex/pattern discovery/lecture05.tex
Технические доработки в документе

\subsubsection{Redundancy-Aware Top-k Patterns}
\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{desired_patterns.png}
    \caption{Desired patterns: high significance \& low redundancy}
\end{figure}

@@

\subsubsection{Robustness of Colossal Patterns}
\textbf{Definition.} For a frequent pattern $\alpha$, a subpattern $\beta$ is a $\mathbf{\tau}$\textbf{-core pattern} of $\alpha$ if $\beta$ shares a similar support set with $\alpha$, i.e., 
\begin{equation*}
\frac{\abs{D_\alpha}}{\abs{D_\beta}} \geqslant \tau, 0 < \tau \leqslant 1, 
\end{equation*}
where $\tau$ is called the \textbf{core ratio}.\\

\textbf{Definition.} \textbf{$\mathbf{(d, \tau)}$-robustness}\footnote{Robustness - прочность}: a pattern $\alpha$ is $(d, \tau)$-robust if d is the maximum number of items that can be removed from $\alpha$ for the resulting pattern to remain a $\tau$-core pattern of $\alpha$:
\begin{equation*}
d = \max_{\beta}\{\abs{\alpha} - \abs{\beta} \mid \beta \subseteq \alpha\text{, and }\beta\text{ is a }\tau\text{-core pattern of }\alpha\}
\end{equation*}

@@

\textbf{Theorem.} For a $(d, \tau)$-robust pattern $\alpha$:
\begin{equation*}
\abs{C_\alpha} \geqslant 2^d
\end{equation*}

@@

\textbf{Theorem.} For two patterns $\beta_1, \beta_2 \in C_\alpha$ 
\begin{equation*}
Dist(\beta_1, \beta_2) \leqslant r(\tau)\text{, where }r(\tau)=1-\frac{1}{2/\tau-1}
\end{equation*}

>>>>

\subsubsection{Redundancy-Aware Top-k Patterns}

\begin{figure}[h]
\centering
\subfigure[a set of patterns]{%
  \includegraphics[width=0.32\linewidth, height=0.2\linewidth]{desired_patterns_1.png}
  \label{fig:desired1}}
\quad
\subfigure[redundancy-aware top-k]{%
  \includegraphics[width=0.32\linewidth, height=0.2\linewidth]{desired_patterns_2.png}
  \label{fig:desired2}}
\subfigure[traditional top-k]{%
  \includegraphics[width=0.32\linewidth, height=0.2\linewidth]{desired_patterns_3.png}
  \label{fig:desired3}}
\quad
\subfigure[summarization]{%
  \includegraphics[width=0.32\linewidth, height=0.2\linewidth]{desired_patterns_4.png}
  \label{fig:desired4}}
%
\caption{Desired patterns: high significance \& low redundancy}
\label{fig:desired}
\end{figure}

@@

\subsubsection{Robustness of Colossal Patterns}
\begin{definition}
For a frequent pattern $\alpha$, a subpattern $\beta$ is a $\mathbf{\tau}$\textbf{-core pattern} of $\alpha$ if $\beta$ shares a similar support set with $\alpha$, i.e., 
\begin{equation*}
\frac{\abs{D_\alpha}}{\abs{D_\beta}} \geqslant \tau, 0 < \tau \leqslant 1, 
\end{equation*}
where $\tau$ is called the \textbf{core ratio}.
\end{definition}

\begin{definition}
\textbf{$\mathbf{(d, \tau)}$-robustness}\footnote{Robustness - прочность}: a pattern $\alpha$ is $(d, \tau)$-robust if d is the maximum number of items that can be removed from $\alpha$ for the resulting pattern to remain a $\tau$-core pattern of $\alpha$:
\begin{equation*}
d = \max_{\beta}\{\abs{\alpha} - \abs{\beta} \mid \beta \subseteq \alpha\text{, and }\beta\text{ is a }\tau\text{-core pattern of }\alpha\}
\end{equation*}
\end{definition}

@@

\begin{theorem}
For a $(d, \tau)$-robust pattern $\alpha$:
\begin{equation*}
\abs{C_\alpha} \geqslant 2^d
\end{equation*}
\end{theorem}

@@

\begin{theorem}
For two patterns $\beta_1, \beta_2 \in C_\alpha$ 
\begin{equation*}
Dist(\beta_1, \beta_2) \leqslant r(\tau)\text{, where }r(\tau)=1-\frac{1}{2/\tau-1}
\end{equation*}
\end{theorem}

### 2015-02-22 zoldatoff/tex/pattern discovery/lecture06.tex
Уточнены формулы в разделе "Mining colossal patterns"
* Добавлены формулы из статьи «Mining Colossal Frequent Patterns by
Core Pattern Fusion»
* мелкие правки по форматированию
Технические доработки в документе

Method to find meta-rules:
\begin{itemize}
\item Find frequent (l + r) predicates (based on min-support)
\item Push constants deeply when possible into the mining process
\item Also, push min\_conf, min\_correlation, and other measures as early as possible (measures acting as constraints)
\end{itemize}

@@

A constraint c is \textbf{monotone}: if an itemset S satisfies the constraint \textbf{c}, so does any of its superset. That is, we do not need to check \textbf{c} in subsequent mining. For example, constraints $\sum(S.price) \geqslant v$ or $\min(S.price) \leqslant v$ are monotone.

@@

\textbf{Convertible constraints}: convert tough\footnote{Tough - жесткий} constraints into (anti-)monotone by proper ordering of items in transactions. For example, ordering items in value-descending order makes the constraint $avg(S.profit) > 20$ anti-monotone \textit{if the patterns grow in the right order}.

>>>>

Method to find meta-rules:
\begin{itemize}
\item Find frequent (l + r) predicates (based on min-support)
\item Push constraints deeply when possible into the mining process
\item Also, push min\_conf, min\_correlation, and other measures as early as possible (measures acting as constraints)
\end{itemize}

@@

A constraint c is \textbf{monotone}: if an itemset S satisfies the constraint \textbf{c}, so does any of its superset. That is, we do not need to check \textbf{c} in subsequent mining. For example, constraints $\mathrm{sum}(S.price) \geqslant v$ or $\min(S.price) \leqslant v$ are monotone.

@@

\textbf{Convertible constraints}: convert tough\footnote{Tough - жесткий} constraints into (anti-)monotone by proper ordering of items in transactions. For example, ordering items in value-descending order makes the constraint $\mathrm{avg}(S.profit) > 20$ anti-monotone \textit{if the patterns grow in the right order}.
